Spectral Experts for Estimating Mixtures of Linear Regressions

### 2013-06-11 doc/icml-presentation/presentation.tex
Solved jittery and citation problems

\usepackage{listings}

@@

  \splitcolumn{%
    \begin{itemize} 
      \item {\bf Generative Models} \tikzmark{gen}
        \uncover<2->{%
        \begin{itemize}
          \item Gaussian Mixture Models
          \item Hidden Markov Models
          \item Latent Dirichlet Allocation
          \item PCFGs
          \item \dots
        \end{itemize}
        }
      \item<3-> {\bf Discriminative Models} \tikzmark{disc}
        \uncover<4->{%
        \begin{itemize}
          \item Mixture of Experts
          \item Latent CRFs
          \item Discriminative LDA
          \item \dots
          \item {\em Easy to include features and tend to be more accurate.}
        \end{itemize}
        }
      \end{itemize}
  }{%
  \begin{tikzpicture}[remember picture, overlay]
    \draw[use as bounding box] (current page.north west) rectangle (current page.south east);
    \point{mark}{(2cm,0)};
    \point{gen}{(pic cs:gen)};
    \point{disc}{(pic cs:disc)};
    \point{a}{((pic cs:gen) -| mark)};
    \point{b}{((pic cs:disc) -| mark)};
    %\node<1-> at (a) {\includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/gen.png}};
    %\node<1-> at (b) {\includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/disc.png}};
  \end{tikzpicture}
  }

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,-1.5) {\objw{12cm}{%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood.png}
    \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mle.png}
    \includegraphics<3>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-em.png}
    \includegraphics<4>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      \hfill{\em expected negative log-likelihood}
      }};
  \end{tikzpicture}

@@

\begin{frame}
  \frametitle{Aside: Tensor Operations}
  \begin{tikzpicture}
    % x, y
    \node<1->[style=box] (defn) at (0,0) {\objw{6cm}{%
    \begin{align*}
        \action<1->{%
        x\tp{3}_{ijk} &= x_i x_j x_k \comment{tensoring}\\
        }
        \action<2->{%
        \innerp{A}{B} &= \sum_{ijk} A_{ijk} B_{ijk} \comment{inner product}\\
        }
        \action<3->{%
        A(u)_{ij} &= \sum_{k} A_{ijk} u_k \comment{projection}\\
        }
        \action<4->{%
        A(u,v)_{i} &= \sum_{jk} A_{ijk} u_j v_k \comment{projection} \\
        }
      \end{align*}
    }};
    \tikzcube{black,fill=white}{(6,2,0)}{1}{1}{1};
    %\node (pt) at (5.75,1.75,0) {$\hlmath{\times}$};
    \uncover<3->{%
    \tikzrect{black,fill=white}{(6,0)}{1}{1};
    }
    \uncover<4->{%
    \tikzrect{black,fill=white}{(6,-2)}{0.1}{1};
    }
  \end{tikzpicture}

@@

\begin{frame}
  \frametitle{Example: Gaussian Mixture Model}
  \begin{tikzpicture}
    % x, y
    \node<1->[style=box] (moments) at (0,0) {\objw{6cm}{%
      If $\beta_h$ are orthogonal;
      \begin{align*}
        \E[x\tp{3}] &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
      \end{align*}
    }};
    \node<1->[style=box] (models) at (6,0) {\objw{6cm}{%
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/gen.png}
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.png}
    }};

    \node<1-> at (6,-3) {\objw{6cm}{%
    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor.png}
      }};
    \node<2->[style=box] at (0,-3) {\objw{6cm}{%
      $\beta_h$ are eigenvectors!
        \begin{align*}
          \E[x\tp{3}](\beta_h,\beta_h) 
            %&= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
            %&= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
            &= \pi_{h} \beta_{h}.
        \end{align*}

        \hfill{\em Anandkumar, Hsu, et.\ al (2012)}
      }};
%
%    \node<2>[style=box,below=0.1cm of tensorf] {\objw{12cm}{%
%    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor-decomp.png}
%      \hfill {Tensor Power Method}
%      }};
  \end{tikzpicture}
\end{frame}

>>>>

\usepackage{listings}
\usepackage[style=verbose,autocite=footnote,maxnames=10,babel=hyphen,hyperref=true,abbreviate=false,mcite]{biblatex}
\addbibresource{ref.bib}

@@

  \splitcolumn{%
    \begin{itemize} 
      \item {\bf Generative Models} \tikzmark{gen}
        \uncover<2->{%
        \begin{itemize}
          \item Gaussian Mixture Models
          \item Hidden Markov Models
          \item Latent Dirichlet Allocation
          \item PCFGs
          \item \dots
        \end{itemize}
        }
      \item<3-> {\bf Discriminative Models} \tikzmark{disc}
        \uncover<4->{%
        \begin{itemize}
          \item Mixture of Experts
          \item Latent CRFs
          \item Discriminative LDA
          \item \dots
          \item {\em Easy to include features and tend to be more accurate.}
        \end{itemize}
        }
      \end{itemize}
  }{%
  \begin{tikzpicture}[remember picture, overlay]
    \draw[use as bounding box] (current page.north west) rectangle (current page.south east);
    \point{mark}{(3cm,0)};
    \point{gen}{(pic cs:gen)};
    \point{disc}{(pic cs:disc)};
    \point{a}{(gen -| mark)};
    \point{b}{(disc -| mark)};
    \node<1->[anchor=north east] at (a) {\includegraphics[width=\textwidth,height=2cm,keepaspectratio]{figures/gen.png}};
    \node<3->[anchor=north east] at (b) {\includegraphics[width=\textwidth,height=2cm,keepaspectratio]{figures/disc.png}};
  \end{tikzpicture}
  }

@@

  \begin{tikzpicture}
    % x, y
    \node at (0,-1.5) {%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood.png}
    \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mle.png}
    \includegraphics<3>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-em.png}
    \includegraphics<4>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      };
  \end{tikzpicture}

@@

\begin{frame}
  \frametitle{Aside: Tensor Operations}
  \twocolumn{%
    \begin{align*}
        \action<1->{%
        \tikzmark{tensoring}x\tp{3}_{ijk} &= x_i x_j x_k \comment{tensoring}\\
        }
        \action<2->{%
        \tikzmark{innerp}\innerp{A}{B} &= \sum_{ijk} A_{ijk} B_{ijk} \comment{inner product}\\
        }
    \end{align*}
  }{%
  \begin{tikzpicture}[remember picture, overlay]
    \draw[use as bounding box] (current page.north west) rectangle (current page.south east);
    \point{mark}{(4cm,0)};
    \point{tensoring}{(pic cs:tensoring)};
    \point{innerp}{(pic cs:innerp)};
    \point{a}{(tensoring -| mark)};
    \point{b}{(innerp -| mark)};
      \tikzcube{black,fill=white}{($(a) + (0,0,0)$)}{1}{1}{1};
      \tikzcube{black,fill=white}{($(b) + (0,0,0)$)}{1}{1}{1};
    \end{tikzpicture}
  }
\end{frame}

@@

\begin{frame}
  \frametitle{Example: Gaussian Mixture Model}
  \twocolumn{%
    \begin{itemize}
      \item If $\beta_h$ are orthogonal;
      \begin{align*}
        \E[x\tp{3}] &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
      \end{align*}
      \item<2-> $\beta_h$ are eigenvectors \footcite{AnandkumarGeHsu2012}!
        \begin{align*}
          \E[x\tp{3}](\beta_h,\beta_h) 
            %&= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
            %&= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
            &= \pi_{h} \beta_{h}.
        \end{align*}
    \end{itemize}
  }{%
  %\begin{tikzpicture}
  %  % x, y
  %  \node<1->[style=box] (models) at (6,0) {\objw{6cm}{%
  %    \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/gen.png}
  %    \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.png}
  %  }};
  %  \node<1-> at (6,-3) {\objw{6cm}{%
  %  \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor.png}
  %    }};
  %\end{tikzpicture}
  }
\end{frame}
